The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-06-19 paper.tex
update acknowledgement

\begin{ack}
\noindent\begin{minipage}{0.90\textwidth}
We gratefully acknowledge Laura Penne for her valuable support in data acquisition and the conception and design of the input format.
We would like to express our sincere thanks to Andrea Ferencová and Hanjo Tim Fritzsch for their contributions to data acquisition.
Additionally, we extend our gratitude to Marleen Mohaupt, Andy Ludwig and Niklas de Sousa Norte for their contributions to data acquisition and project support.
The ANNO project is co-financed from tax funds based on the budget passed by the Parliament of the Free State of Saxony.

>>>>

\begin{ack}
\noindent\begin{minipage}{0.90\textwidth}
We gratefully acknowledge Laura Penne for her valuable support in data acquisition and the conception and design of the content and input format.
We would also like to express our sincere thanks to Hanjo Tim Fritzsch, Niklas de Sousa Norte, and Andrea Ferencová for their contributions to data acquisition.
Additionally, we extend our gratitude to Marleen Mohaupt and Andy Ludwig for their contributions to the project's execution.
The ANNO project is co-financed from tax funds based on the budget passed by the Parliament of the Free State of Saxony.
